\begin{center}
{\large\textbf{ACKNOWLEDGEMENTS}}
\end{center}

\onehalfspacing

This thesis is a work of a long journey for five and a half year. It has been an eventful ride where I met numerous people, with each
leaving some impression on my professional or personal life. I would like to take this place to acknowledge these people.

%For Brajesh Sir,
First and foremost, I would like to express my gratitude to my thesis supervisor Prof. Brajesh Chandra Choudhary for providing support 
and expertise. I am really grateful to him for providing the opportunity to work with the CMS experiment at the European Organization 
for Nuclear Research. His guidance over the years has proved most valuable for my shaping as a researcher. His enthusiasm about the results, 
whether positive or negative, has been a continous source of motivation and encouragement. I also learnt from him the importance of being 
organized and having a professional attitude in research.
  
%%For Debajyoti Sir
I would like to thank my co-supervisor Prof. Debajyoti Choudhury for his invaluable suggestions and comments during my research work.
For the innumerable interactions I had with him, whether brief or extended, it always made me ever more motivated and passionate as his deep insight into physics
and desire to search for new ideas has always been a source of encouragement. I would also like to thank both my supervisors for their thorough review and 
patience over my research period and especially during the preparation of this thesis over the last few months.

%%Advisory committee
Many thanks to my Ph.D advisory committee members, Prof. Amitabha Mukherjee and Dr. Samit Mandl, for giving me constructive suggestions and comments at different stages
of my Ph.D.

%%% For Sushil
I owe a sincere thank to Dr. Sushil Singh Chauhan with whom I closely worked, during my Ph.D tenure. I am grateful for his help, both fundamental and technical,
to learn about the software and analysis aspects. Many thanks to Prof. Robert Harris for carefully reviewing the analysis and his invaluable suggestions to improve 
the final results. I would also like to acknowledge the fruitful discussions with Dr. John Paul Chou and Dr. Dinko Ferencek on several aspects of this analysis. A 
vote of thanks to members of the CMS collaboration and people involved in this analysis directly or indirectly at different stages of the analysis.

%% CDRST Faculty
I would like to thank everyone in the Experimental High Energy Physics group at the University of Delhi, Prof. R. K. Shivpuri, Dr. Kirti Ranjan, Dr. Md. Naimuddin, 
Dr. Ashok Kumar, Dr. Ashutosh Bhardwaj, and Dr. Satyaki Bhattacharya (now at SINP) for their valuable support during my Ph.D tenure. 
%%Advisory committee
I am obliged to Prof. Amitabha Mukherjee (Head, Department of Physics \& Astrophysics) for providing adequate facilities in the department.
I would also like to acknowledge fellow colleagues and faculty members of the India-CMS collaboratons for their valuable discussions and suggestions during the 
collaboration meetings and otherwise.

%%For CDRST lab
I would like to thank my seniors who have all graduated and fellow colleagues at our research lab at the University of Delhi, consisting of Dr. Sudha Ahuja, Dr. Sandhya Jain, 
Dr. Shilpi Jain, Dr. Arun Kumar, Dr. Raman Khurana, Dr. Daljeet Kaur, Ranjeet Dalal, Shivali Malhotra, Ajay Kumar, Pavanpoot Pandey, Rocky Singla, Ram Krishna Sharma, 
Prabjhot Singh, Sumit Kesri, Ankit Gaur, Priyanka Phogat, Geetika Jain, Aashaq Hussain Shah, Aman Phogat, Mohit Gola, Zuber Ahmad Dar, Mohd. Rafik, Prajesh Sharma, few of 
whom are also good friends.
%%For Lab staff
Many thanks to the staff of CDRST lab, Mohd. Yunus, Sanjay Singh, and Aamir Husain for their innumberable help.

%%
%%Funding agencies
I would like to acknowledge the taxpayers of India and across the globe, whose silent contributions made this experiment possible through the grants from
UGC, DAE-DST (Govt. of India) and funding agencies of all the collaborating nations. I would also like to thank the organizers of various summer schools, viz., 
SUSSP69 (St. Andrews, UK), $8^{th}$ MCnet (Ambelside, UK), Sakura Exchange Program (Osaka, Japan) for inviting and providing necessary financial support for these 
programs. A special thank to Prof. Silvia Pascoli for inviting me to IPPP, Durham University, UK for research related work and ensuring my pleasant stay at Durham.

  
%%My childhood friends
I would like to acknowledge my best buddies, Vivek Rajawat, Abhishek Rajawat, Sachin Bhatija, for their support through these years.
I thank them for numerous cheerful and unforgettable moments we have shared together.
%%
%% For Bhawna
I am thankful to the special person in my life Dr. Bhawna Gomber for being around (virtually) all these years. Many thanks for her love, care, support and patience
despite the difficult times.
%that special person in my life who has been there 
%A heartiest acknowledgement goes to the girl in my life. 

%% For Family
Finally, my deepest gratitude goes to my loving parents, who mean the world to me. I am and will always be indebted to them for all the sacrifies they have made for me. 
This thesis would have simply been impossible without their understanding, endless patience and constant encouragement. A big thank to all my cousin brothers 
and sisters for their continous love and support through these years, with special mention to little cousin Aarav Dogra. 

%%
\begin{flushright}
{\large Varun Sharma}
\end{flushright}

\onehalfspacing
