\begin{center}
\doublespacing
{\Large \textbf{ DECLARATION}}
\vspace{0.8cm}
\end{center}
It is certified that the work presented in this thesis entitled ``{\bf Search for excited quarks at $\sqrt{s}=8\unit{TeV}$ with the CMS Experiment at the Large Hadron
Collider}" has been carried out at the Department of Physics \nd Astrophysics of the University of Delhi under the supervision of Prof. Brajesh Chandra Choudhary and 
Prof. Debajyoti Choudhury. This thesis deals with the search of excited quarks in the photon + jet final states at 8 TeV with 19.7 \fbinv of proton$-$proton collision
data collected by the CMS Experiment at the Large Hadron Collider at European Organization for Nuclear Research (CERN), Geneva, Switzerland.

This work has been done by the candidate himself and, to the best of his knowledge, no part of this work has earlier been submitted for any degree or diploma of this or any other university.
\vspace{0.4 in}	

\begin{flushright}
\doublespacing
Varun Sharma\\
(Candidate)\\
\end{flushright}

%\vspace{0.2 in}	

\begin{flushleft}
\doublespacing
Prof. Brajesh Chandra Choudhary\\
(Supervisor)\\
\end{flushleft}

\vspace{0.3 in}	

\begin{flushleft}
\doublespacing
Prof. Debajyoti Choudhury\\
(Co-Supervisor)\\
\end{flushleft}


\vspace{1 cm}	
\begin{center}
\doublespacing
{\large Prof. Amitabha Mukherjee}\\
%{\large Head}\\
%{\large Head of the Department}\\
{\large Head, Department of Physics \& Astrophysics}\\
{\large University of Delhi}\\
{\large Delhi 110 007}\\
\end{center}


