\begin{center}
\doublespacing
{\Large \textbf{LIST OF PUBLICATIONS}}
\end{center}
{\Large \textbf{Journal Publication:}}
\begin{enumerate}
{%\large
\item ``Search for excited quarks in the \gamjet final state in proton$-$proton collisions at \sqrteighttev'', B. C. Choudhary ...{\bf Varun Sharma} ...\emph{et. al.} [CMS Collaboration]. \\ {\bf Physics Letters B 738 (2014) 274-293}.
}
\end{enumerate}
%
\vspace{0.3cm}
{\Large \textbf{Other Public Results:}}
\begin{enumerate}
{%\large 
\item ``Search for excited quarks in the photon + jet final state in proton$-$proton collisions at \sqrteighttev'', B. C. Choudhary ...{\bf Varun Sharma} ...\emph{et. al.} [CMS Collaboration]. \\ {\bf CMS PAS EXO-13-003 (Public Analysis Summary)}.
}
\end{enumerate}
%
\vspace{0.3cm}
{\Large \textbf{CMS Analysis Notes:}}
\begin{enumerate}
{%\large 
\item ``Search for excited quarks in the photon$+$jet final state in $pp$ collisions at \sqrteighttev$\,$ in the CMS experiment with 19.7\fbinv of data'', 
       Sushil Singh Chauhan, Brajesh Choudhary, Debajyoti Choudhury, {\bf Varun Sharma}, Mani Tripathi. \\
      {\bf CMS Analysis Note-13-218 (2013)}.

\item ``Search for excited b-quarks in the b-tagged \gamjet final state at 8 TeV'', Brajesh Choudhary, Rocky Bala Garg, {\bf Varun Sharma}. \\
       {\bf CMS Analysis Note-15-039 (2015).}      

\item ``Search for excited quark resonance using the photon$+$jet mass spectrum with 2.5\fbinv of proton-proton collision data at $\sqrtthirteentev\,$ in the CMS experiment.''
       Sushil Singh Chauhan, Brajesh Choudhary, Rocky Bala Garg, {\bf Varun Sharma}, Mani Tripathi. \\
      {\bf CMS Analysis Note-15-262 (2015)}.

}
\end{enumerate}
%
\vspace{0.3cm}
{\Large \textbf{Conference Proceedings/Poster Presentations:}}
\begin{enumerate}
{%\large
\item ``Search for an excited quark resonance decaying to a photon and a jet at the CMS'', {\bf Varun Sharma}. \\
       Poster presented at the {\bf Eight MCnet School}, held at Ambleside (Lake District), UK, 24$-$30 August 2014.

\item ``Resonance search for quark excitation with the CMS experiment, {\bf Varun Sharma}. \\
       Poster presented at the {\bf 37$^{th}$ International Conference on High Energy Physics} held at Valencia, Spain, 2-9 July 2014. \\
       To be published in Nuclear and Particle Physics Proceedings.

\item ``Search for excited quarks in the \gamjet final state in proton proton collisions at 8\unit{TeV}'', {\bf Varun Sharma}. \\
       Poster presented at the {\bf LHC Experiments Committee meeting poster session (LHCC)} held at CERN, Switzerland, 5$^{th}$ March 2014. 

\item ``Search for Quark Compositeness'', {\bf Varun Sharma}. \\ 
       Poster presented at the {\bf 69$^{th}$ Scottish Universities Summer School in Physics} held at St. Andrews, Scotland, 19$^{th}$ August $-$ 1$^{st}$ September 2012.
}       
\end{enumerate}








